---
title: "01-model"
output: html_document
---

```{r setup, include=FALSE}
options(scipen = 999)
library(tidyverse)
library(tidymodels)

# update rcfss if the package is not up-to-date - only way to access bechdel
# remotes::install_github("uc-cfss/rcfss")
library(rcfss)

data("bechdel")
bechdel
```

# Your Turn 1

Run the chunk below and look at the output. Then, copy/paste the code and edit to create:

+ a decision tree model for classification 

+ that uses the `C5.0` engine. 

Save it as `tree_mod` and look at the object. What is different about the output?

*Hint: you'll need https://www.tidymodels.org/find/parsnip/*

```{r}
lr_mod <- logistic_reg() %>% 
  set_engine(engine = "glm") %>% 
  set_mode("classification")
lr_mod
```

```{r}

```

# Your Turn 2

Fill in the blanks. 

Use `initial_split()`, `training()`, and `testing()` to:

1. Split **bechdel** into training and test sets. Save the rsplit!

2. Extract the training data and fit your classification tree model.

3. Predict the testing data, and save the true `bechdel` values.

4. Measure the accuracy of your model with your test set.  

Keep `set.seed(100)` at the start of your code.

*Hint: Be sure to remove every `_` before running the code!*

```{r}
set.seed(100) # Important!

bechdel_split  <- ________(data = bechdel, strata = bechdel, prop = 3/4)
bechdel_train  <- ________(bechdel_split)
bechdel_test   <- ________(bechdel_split)

________ %>% 
  fit(bechdel ~ metascore + imdb_rating, 
      data = ________) %>% 
  predict(new_data = ________) %>% 
  mutate(true_bechdel = ________) %>% 
  accuracy(truth = ________, 
           estimate = .pred_class)
```

## Your Turn 3

What would happen if you repeated this process? Would you get the same answers?

Note your accuracy from above. Then change your seed number and rerun just the last code chunk above. Do you get the same answer? 

Try it a few times with a few different seeds.

## Your Turn 4

Run the code below. What does it return?

```{r}
set.seed(100)
bechdel_folds <- vfold_cv(data = bechdel_train, v = 10, strata = bechdel)
bechdel_folds
```

## Your Turn 5

Modify the code below to use `fit_resamples` and `bechdel_folds` to cross-validate the classification tree model. What is the ROC AUC that you collect at the end?

```{r}
set.seed(100)
tree_mod %>% 
  fit(bechdel ~ metascore + imdb_rating, 
      data = bechdel_train) %>% 
  predict(new_data = bechdel_test) %>% 
  mutate(true_bechdel = bechdel_test$bechdel) %>% 
  accuracy(truth = true_bechdel, estimate = .pred_class)
```
